Deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-05-06 paper.tex
Commit from GitHub Actions (Render R Markdown)

Various versions of this software have been used in several recently
published and not-yet-published works by the author of this paper, all
of which are available in the \texttt{examples} folder in the source
code repository
\href{https://github.com/simplymathematics/deckard}{here}. One published
work, now reproducible via the \texttt{examples/attack\_defence\_survey}
folder, includes a large survey of attacks and defences against
canonical datasets and models (C. Meyers, Löfstedt, and Elmroth 2023).
Another work analysed the run-time requirements of attacks against a
particular model before and after retraining against those attacks (C.
Meyers, Löfstedt, and Elmroth 2024) (reproducible via
\texttt{examples/retraining}). The next paper formalised a method for
estimating the time-to-failure of a given model against a suite of
attacks and introduce a metric that quantifies the ratio of attack and
training cost (Meyers et al. 2023) (reproducible via
\texttt{examples/survival\_heuristic}). Furthemore, a not yet published
work uses this time-to-failure model as a mechanism for analysing the
cost efficacy of various hardware choices in the context of adversarial
attacks (reproducible via \texttt{examples/power}) (C. Meyers et al.
2024). Another work exploits the tooling to train a custom model that is
designed to run client-side by using compression algorithms to measure
the distance between text (reproducible via
\texttt{examples/compression}).

@@

For ML, various regulatory and legal frameworks govern safety (The
Parliament of the European Union 2024; {``{ISO} 26262-1:2011, Road
Vehicles --- Functional Safety''} 2018; \emph{IEC 61508 Safety and
Functional Safety} 2010; \emph{IEC 62304 Medical Device Software -
Software Life Cycle Processes} 2006), privacy {[}The Parliament of the
European Union (2024);European Parliament and Council of the European
Union (2016);Legislature of the United States (1996);Legislature of the
United States (1998);{]} and/or transparency (The Parliament of the
European Union 2024; The Legislature of California 2024). The software
package presented here provides a machine- and human-readable format for
creating reproducible and auditable experiments as required by various
regulations. In addition, several examples connected to both published
and not-yet-published work live in the \texttt{examples} folder in the
repository, allowing for easy reproducibility of several extensive sets
of experiments across several popular ML software frameworks. The
\texttt{power} example provides a reproducible way to run a suite of
adversarial tests using popular cloud-based platforms and the
\texttt{retraining} and \texttt{survival\_heuristic} examples provide
examples of both CPU and GPU-based parallelisation, respectively.

>>>>

Various versions of this software have been used in several recently
published and not-yet-published works by the author of this paper, all
of which are available in the \texttt{examples} folder in the source
code repository \url{https://github.com/simplymathematics/deckard}. One
published work, now reproducible via the
\texttt{examples/attack\_defence\_survey} folder, includes a large
survey of attacks and defences against canonical datasets and models (C.
Meyers, Löfstedt, and Elmroth 2023). Another work analysed the run-time
requirements of attacks against a particular model before and after
retraining against those attacks (C. Meyers, Löfstedt, and Elmroth 2024)
(reproducible via \texttt{examples/retraining}). The next paper
formalised a method for estimating the time-to-failure of a given model
against a suite of attacks and introduce a metric that quantifies the
ratio of attack and training cost (Meyers et al. 2023) (reproducible via
\texttt{examples/survival\_heuristic}). Furthemore, a not yet published
work uses this time-to-failure model as a mechanism for analysing the
cost efficacy of various hardware choices in the context of adversarial
attacks (reproducible via \texttt{examples/power}) (C. Meyers et al.
2024). Another work exploits the tooling to train a custom model that is
designed to run client-side by using compression algorithms to measure
the distance between text (reproducible via
\texttt{examples/compression}).

@@

For ML, various regulatory and legal frameworks govern safety (The
Parliament of the European Union 2024; {``{ISO} 26262-1:2011, Road
Vehicles --- Functional Safety''} 2018; \emph{IEC 61508 Safety and
Functional Safety} 2010; \emph{IEC 62304 Medical Device Software -
Software Life Cycle Processes} 2006), privacy (The Parliament of the
European Union 2024; European Parliament and Council of the European
Union 2016; Legislature of the United States 1996, 1998) and/or
transparency (The Parliament of the European Union 2024; The Legislature
of California 2024). The software package presented here provides a
machine- and human-readable format for creating reproducible and
auditable experiments as required by various regulations. In addition,
several examples connected to both published and not-yet-published work
live in the \texttt{examples} folder in the repository, allowing for
easy reproducibility of several extensive sets of experiments across
several popular ML software frameworks. The \texttt{power} example
provides a reproducible way to run a suite of adversarial tests using
popular cloud-based platforms and the \texttt{retraining} and
\texttt{survival\_heuristic} examples provide examples of both CPU and
GPU-based parallelisation, respectively.
